Modeling Time-Variable Elemental Abundances in Coronal Loop Simulations

### 2024-06-08 src/tex/ms.tex
[showyourwork] overleaf sync
[showyourwork]

\begin{acknowledgements}
At the time of writing, the implementation into \texttt{ebtel++} is publicly available as an unmerged pull request on GitHub: \url{https://github.com/rice-solar-physics/ebtelPlusPlus/pull/87}.  This paper is fully reproducible with the \texttt{showyourwork!} package, and can be downloaded from \url{https://github.com/jwreep/ebtel_abundances}.  
\end{acknowledgements}

>>>>

\section*{Acknowledgments}
At the time of writing, the implementation into \texttt{ebtel++} is publicly available as an unmerged pull request on GitHub: \url{https://github.com/rice-solar-physics/ebtelPlusPlus/pull/87}.  This paper is fully reproducible with the \texttt{showyourwork!} package, and can be downloaded from \url{https://github.com/jwreep/ebtel_abundances}.
